Measuring contrast processing in the visual system using SSVEP

### 2024-04-25 review.qmd
Attention

SSVEP and psychophysical measurements of attentional effects on both luminance and chromatic contrast strongly implicated gain control an an underlying mechanism [@DiRusso2001GainControl, @lu1998external].  In the late 2000s a comprehensive theoretical model for attentional modulation was developed that framed it as a gain control computation (Reynolds and Heeger 2009, Boynton Vis Res 2009). This framework has proven to be influential - explaining a wide range of phenomena from the earlier literature and demonstrating subtle interactions between the size of the attentional 'spotlight' and the stimulus configuration which rationalise many apparent contradictions in the literature. Subsequent papers   (effect of stimulus configuration critical). Then... talk about Lauriten et al, Verghese (2 papers) maybe mention Crognale / Highsmith, Wang+Wade and Jasna's paper from 2018. https://www.sciencedirect.com/science/article/abs/pii/S1053811918303860) Probably lots more Carasco ...

>>>>

Electrophysiological and psychophysical measurements of attentional effects on both luminance and chromatic contrast strongly implicated gain control an an underlying mechanism [@dirusso99Attention, @DiRusso2001GainControl, @lu1998external] and demonstrated that these effects differed between chromatic and achromatic pathways [@dirusso1999mcpc].  In the late 2000s a comprehensive theoretical model for attentional modulation was developed that framed it as a gain control computation (Reynolds and Heeger 2009, Boynton Vis Res 2009). This framework has proven to be influential - explaining a wide range of phenomena from the earlier literature and demonstrating subtle interactions between the size of the attentional 'spotlight' and the stimulus configuration which rationalise many apparent contradictions in the literature. Subsequent papers   (effect of stimulus configuration critical). Then... talk about Lauriten et al, Verghese (2 papers) maybe mention Crognale / Highsmith, Wang+Wade and Jasna's paper from 2018. https://www.sciencedirect.com/science/article/abs/pii/S1053811918303860) Probably lots more Carasco ...
